Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex
Updates from Overleaf

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}.
Rule based approaches look for portions of text that match patterns based on word characteristics such as their case, their part-of-speech tags, etc.
These patterns can be fully handcrafted like in \cite{bell2020automated} or generated by data mining approaches like in \cite{nouvel2011}.
Rule based approaches can also combine a set of patterns with a set of dictionaries (gazetteers, author lists, etc.) that help recognizing named entities when an exhaustive lexicon of searched entities is available \cite{mansouri2008,maurel2011}.
%For example, the CasEN\footnote{\url{https://tln.lifat.univ-tours.fr/version-francaise/ressources/casen}} transducer cascade leverages syntactic lexical patterns and dictionaries to recognize Named Entities in French texts.
Such kind of approaches achieve very good results when applied to specialized domain corpus - like directories - and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify tokens into named entity categories.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances and establishing new baselines\cite{li2020}.
A recent survey proposed by \cite{li2020} presents deep learning techniques for NER according to the distributed representation(s) they use as input, their context encoder and their tag decoder.
It shows that language model embeddings pretrained using \textit{Transformer} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, can not only be used to replace traditional embeddings as input distributed representations but also be fine-tuned for the NER task with one additional output layer while achieving state-of-the-art performances.
The survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data.

\subsection{Named Entity Recognition on historical texts}
\label{subsection:stoa-ner-on-historical-texts}
\cite{Labusch2020NamedED} pretrained an off-the-shelf multilingual BERT-based NER model on more than 2 000 000 pages of OCRed historical texts in German, French, and English. They fine-tuned it on historical texts NER ground truth, also in these three languages and tested it on OCRed historical texts in each language.
Eventually, a clear decrease in NER performance on OCRed texts is noted, especially for the English texts for which the OCR is of poorer quality.

@@

\subsubsection{Transformers / Bert / Hugging face}
Language model based on Transformers, like BERT, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pretrained in an unsupervised way on historical texts for domain adaptation.
As the directories are written in French, we chose the language model CamemBERT \cite{martin-etal-2020-camembert}, a Transformer model trained on a French corpus.
\joseph{plutôt tourner ça pour dire qu'il existe des modèles FR / qu'on est limités par la dispo de modèles FR pré-entraînés ?}

>>>>

Many approaches have been designed to recognize named entities, ranging from handcrafted rules to supervised approaches \cite{nadeau2007}.
Rule based approaches look for portions of the text that match patterns like in \cite{bell2020automated,nouvel2011} or dictionary (gazetteers, author lists, etc.) entries like in \cite{mansouri2008,maurel2011}.
Such kind of approaches achieve very good results when applied to a specialized domain corpus and when an exhaustive lexicon are available, but at high system engineering cost \cite{nadeau2007}.

Supervised approaches include both approaches implementing supervised learning algorithms with careful text feature engineering, and deep learning based approaches which automatically build their own features to classify tokens into named entity categories.
In recent years, the latter have grown dramatically, yielding state-of-the-art performances as shown in the recent survey proposed by \cite{li2020}. This survey concludes that fine-tuning general-purpose contextualized language models with domain-specific data is very likely to give good performance for use cases with domain-specific texts and few training data. This strategy has been adopted by \cite{Labusch2020NamedED} to extract named entities in OCRed historical texts in German, French, and English. However, the NER performance decreased dramatically with OCRed texts is noted, especially for the English texts for which the OCR is of poorer quality.

\subsection{Improving Named Entity Recognition in historical texts}
\label{subsection:stoa-ner-on-historical-texts}

@@

\subsubsection{Transformers / Bert / Hugging face}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pretrained in an unsupervised way on historical texts for domain adaptation.
As the directories are written in French, we chose the language model CamemBERT \cite{martin-etal-2020-camembert}, a Transformer model trained on a French corpus.
\joseph{plutôt tourner ça pour dire qu'il existe des modèles FR / qu'on est limités par la dispo de modèles FR pré-entraînés ?}
